---
title: "EDR Interview"
author: "Glenn Free"
---

'Setup Chunk'

```{r}
library(DBI)
library(reticulate)
library (readr)

git_url="https://raw.githubusercontent.com/DarthVidarr/Repos/main/SampleDataset.csv"

SampleDataset <-read_csv(url(git_url))

con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")
dbWriteTable(con, "SampleDataset", SampleDataset)
```

'SQL Chunk'

1 How many rows are in the dataset?
2 How many unique Species types are there?
3 What is the average value of Sepal.Length for Species 'setosa'
4 With the exception of 'Species', remove all rows with non-numeric values.
5 How many rows are in the dataset after removing non-numeric values?
6 Are there the same number of rows or less? Why?

```{sql, connection=con, output.var="sql_df"}


```

'R Chunk'

1 How many rows are in the dataset?
2 How many unique Species types are there?
3 What is the average value of Sepal.Length for Species 'setosa'
4 With the exception of 'Species', remove all rows with non-numeric values.
5 How many rows are in the dataset after removing non-numeric values?
6 Are there the same number of rows or less? Why?

```{r}
```

'Python Chunk'

1 How many rows are in the dataset?
2 How many unique Species types are there?
3 What is the average value of Sepal.Length for Species 'setosa'
4 With the exception of 'Species', remove all rows with non-numeric values.
5 How many rows are in the dataset after removing non-numeric values?
6 Are there the same number of rows or less? Why?

```{python}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
